HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-05 scnn.tex
add first version of the conclusion

\section{Experiments}
\label{sec:experiments}

@@

\subsection{Results}
\assign{Nathanaël, Tomek}

@@

\subsection{Filter visualization} 
\assign{Nathanaël, Tomek, Michaël} 
Onecommon visualization for CNN is to display the shape of the learned filters.
Since our construction lead to almost (up to the sampling irregularities)
spherical filters, we plot in \figref{learned_filter} both the section (on the
sphere) and a gnomeview projection on a plane of a random selection of learned
filters. The filters are selected from the last layer of the network
corresponding the experiment with order $o=2$ for a relative noise level of
$2$. Nevertheless, all networks presented similar gnomonic and section pattern, at least from a
human perspective. The gnomonic projection clearly exibits the sampling issue
of HealPix. For a detail, on how the convolution kernels are plot, please refer to
\ref{sec:filter_visualization}. 
\todo{Tomek: can you say something about the filters.}

@@

\section{Conclusion}
\label{sec:conclusion}
\assign{Nathanaël, Tomek, Michaël}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1.pdf}
\caption{Evolution curve of the error with respect of the number of training sample for histogram features and a linear classifier (setting: order 2, relative noise level: 1). The validation error is slightly below the training error because we use the validation set for the cross-validation and hence we are probably slightly overfitting the validation set.}
\label{fig:hist_error_evolution}
\end{figure}

>>>>

\section{Experiments}
\label{sec:experiments}
\assign{Nathanaël, Tomek}

@@

\subsection{Results}

@@

\subsection{Filter visualization} 
Onecommon visualization for CNN is to display the shape of the learned filters.
Since our construction lead to almost (up to the sampling irregularities)
spherical filters, we plot in \figref{learned_filter} both the section (on the
sphere) and a gnomeview projection on a plane of a random selection of learned
filters. The filters are selected from the last layer of the network
corresponding the experiment with order $o=2$ for a relative noise level of
$2$. Nevertheless, all networks presented similar gnomonic and section pattern, at least from a
human perspective. The gnomonic projection clearly exibits the sampling issue
of HealPix. For a detail, on how the convolution kernels are plot, please refer to
\ref{sec:filter_visualization}. 
\todo{Tomek: can you say something about the filters.}

@@

\section{Conclusion}
\label{sec:conclusion}

In this contribution, we presented HealPixNet, a spherical CNN for the HealPix sampling. The gist of our construction reside in using a graph to model the sphere. 
This allows us to leverage the advantages of graph convolution as it is both efficient $\mathcal{O}(n)$ and flexible (allow to work only on a subpart of the sphere) while still well capturing the spherical properties of the domain. 
We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.

We provide HealPixNet as a small easy to use package availlable at \todo{\url{https://github.com/xxx}}. 
As a futur work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1_5.pdf}
\caption{Evolution curve of the error with respect of the number of training sample for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5). The validation error might be slightly below the training error because we use it for cross-validation.}
\label{fig:hist_error_evolution}
\end{figure}
